### 2019-08-13 scache/tii/tex/impl.tex
Fix typos

\subsubsection{Context-Aware-Priority Constraint}
% Unlike the traditional cache replacement schemes such as MIN \cite{min}, the cached shuffle data will only be used once, but the legacy cache managements are designed to improve the hit rate.
{\color{black}
SCache leverages application context to select victim storage units when the reserved memory is full.
At first, SCache flushes blocks of the incomplete units to disk cluster-widely.
If all the units are completed, SCache selects victims based on two factors: 
(a) For the tasks in the different stages, SCache sets the higher priority to storage units with a earlier submission time;
(b) For the tasks in the same stage, SCache sets the higher priority to storage units with a smaller task ID.
}
% If all the units are completed, SCache selects victims based on two factors --- \textit{inter-shuffle} and \textit{intra-shuffle}.
% \begin{itemize}[noitemsep]
% 	\item Inter-shuffle: SCache master follows the scheduling scheme of Spark to determine the inter-shuffle priority. 
% 	% For example, Spark FIFO scheduler schedules the tasks of different stages according to the submission order. 
% 	SCache sets the priorities of tasks according to the submission time of each shuffle.
% 	% For a FAIR scheduler, Spark balances the resource among task sets, which leads to a higher priority for those having more tasks unfinished. 
% 	% So SCache sets priorities from high to low in a descending order of remaining storage units of a shuffle. 
% 	% For a FIFO scheduler, Spark schedules the task set that is submitted first. 
% 	% So SCache sets the priorities according to the submit time of each shuffle unit.
% 	\item Intra-shuffle: The intra-shuffle priorities are determined according to the task scheduling inside a stage.
% 	For example Spark schedules tasks with smaller ID at first. 
% 	Based on this, SCache can assign the lower priority to storage units with a larger task ID.
% \end{itemize}

>>>>

\subsubsection{Context-Aware-Priority Constraint}
% Unlike the traditional cache replacement schemes such as MIN \cite{min}, the cached shuffle data will only be used once, but the legacy cache managements are designed to improve the hit rate.
{\color{black}
SCache leverages application context to select victim storage units when the reserved memory is full.
At first, SCache flushes blocks of the incomplete units to disk cluster-widely.
If all the units are completed, SCache selects victims based on two factors: 
(a) For the tasks in the different stages, SCache sets the higher priority to storage units with an earlier submission time;
(b) For the tasks in the same stage, SCache sets the higher priority to storage units with a smaller task ID.
}
% If all the units are completed, SCache selects victims based on two factors --- \textit{inter-shuffle} and \textit{intra-shuffle}.
% \begin{itemize}[noitemsep]
% 	\item Inter-shuffle: SCache master follows the scheduling scheme of Spark to determine the inter-shuffle priority. 
% 	% For example, Spark FIFO scheduler schedules the tasks of different stages according to the submission order. 
% 	SCache sets the priorities of tasks according to the submission time of each shuffle.
% 	% For a FAIR scheduler, Spark balances the resource among task sets, which leads to a higher priority for those having more tasks unfinished. 
% 	% So SCache sets priorities from high to low in a descending order of remaining storage units of a shuffle. 
% 	% For a FIFO scheduler, Spark schedules the task set that is submitted first. 
% 	% So SCache sets the priorities according to the submit time of each shuffle unit.
% 	\item Intra-shuffle: The intra-shuffle priorities are determined according to the task scheduling inside a stage.
% 	For example Spark schedules tasks with smaller ID at first. 
% 	Based on this, SCache can assign the lower priority to storage units with a larger task ID.
% \end{itemize}

### 2019-08-13 scache/tii/tex/model.tex
Fix typos

% Hadoop MapReduce overlaps shuffle phase with reduce phase and utilizes idle resources. We intuitively think that we can also overlap the shuffle phase and the map phases. We implemented this idea with SCache.
Figure \ref{fig:model_basic} and Figure \ref{fig:model_scache2} shows the scheduling strategy for Hadoop MapReduce with SCache (Suppose N is 4).
SCache also overlap the shuffle phase and the map phases by starting pre-fetching and pre-scheduling in the map phase.
This scheduling strategy avoid the I/O resource being idle in the map phase.
According to the design of SCache pre-fetching, we found that using the FRQ model to describe the scheduling strategy of SCache needs to distinguish two situations:

>>>>

% Hadoop MapReduce overlaps shuffle phase with reduce phase and utilizes idle resources. We intuitively think that we can also overlap the shuffle phase and the map phases. We implemented this idea with SCache.
Figure \ref{fig:model_basic} and Figure \ref{fig:model_scache2} show the scheduling strategy for Hadoop MapReduce with SCache (Suppose N is 4).
SCache also overlap the shuffle phase and the map phases by starting pre-fetching and pre-scheduling in the map phase.
This scheduling strategy avoids the I/O resource being idle in the map phase.
According to the design of SCache pre-fetching, we found that using the FRQ model to describe the scheduling strategy of SCache needs to distinguish two situations:

### 2019-08-13 scache/tii/tex/relatedwork.tex
Fix typos

{\color{black}
\textbf{Modeling} 
% Most representative DAG computing frameworks use similar \textit{Bulk Synchronize Parallel} (BSP)\cite{valiant1990bridging} model to control data synchronization in each computing phase. 
% , i.e., \textit{stage} in Spark, \textit{superstep} in Pregel\cite{malewicz2010pregel} and so on. 
% (Hadoop MapReduce can also be considered as a special case of only one superstep in BSP model). 
% In the process of optimizing the shuffle phases between adjacent computing phases, we design a performance model to assist in analyzing computing process.
% There are also lots of performance models for MapReduce have been proposed, such as \cite{verma2011aria, khan2016hadoop, herodotou2011hadoop, chen2014cresp, farhat2016stochastic}.
% Verma et al. \cite{verma2011aria} proposed the ARIA model to estimate the required resources based on the job information, the amount of input data and a specified soft deadline.
Khan et al. \cite{khan2016hadoop} proposed the HP model which extends the ARIA model. The HP model adds scaling factors and uses a simple linear regression to estimate the job execution time on larger datasets.
% In \cite{herodotou2011hadoop}, Herodotou proposed a detailed set of mathematical performance models for describing the five phases of a MapReduce job and combine them into an overall MapReduce job model.
% The execution is separated into the phases: Read, Map, Collect, Spill, Merge, Shuffle, Merge, and Reduce. 
% The set of performance models describe each above-mentioned phases and combine into an overall MapReduce job model. 
Chen et al. \cite{chen2014cresp} proposed the CRESP model which is a cost model that estimates the performance of a job then 
% provisions the resources for the job.
Farshid Farhat et al.\cite{farhat2016stochastic} proposed a closed-form queuing model which focus on stragglers and try to optimize them. 
% The proposed model is parameterized by the task inter-arrival times to the mappers, the delayed tailed service times, and the number of mappers, which is used to optimize the stragglers. 
% \cite{khan2016hadoop, farhat2016stochastic, chen2014cresp} have proposed several methods to model the DAG computing process.
However, the above models are not able to accurately describe the overhead caused by the shuffle process under different scheduling strategies. 
% Different from these models, our FRQ model quantifies computing and I/O resources and visualizes them in the time dimension. 
The FRQ model focuses on describing the overhead caused by the shuffle process in different scheduling strategies, which satisfies our demand.

@@

\textbf{Pre-scheduling} 
Slow-start from Apache Hadoop MapReduce is a classic approach to handle shuffle overhead. 
% Starfish \cite{starfish} gets sampled data statics for self-tuning system parameters (e.g. slow-start, etc). 
% DynMR \cite{dynmr} dynamically starts reduce tasks in late map stage. 
% All of them have the explicit I/O time in occupied slots. 
% SCache instead starts shuffle pre-fetching without consuming slots. 
iShuffle \cite{guo2017ishuffle} decouples shuffle from reducers and designs a centralized shuffle controller. 
% But it can neither handle multiple shuffles nor schedule multiple rounds of reduce tasks. 
iHadoop \cite{ihadoop} aggressively pre-schedules tasks in multiple successive stages to start fetching shuffle. 
% Besides \textit{slow-start} from Hadoop MapReduce, \cite{starfish, ihadoop, guo2017ishuffle, dynmr} have also proposed several methods to improve the DAG frameworks.
However, we have proved that randomly assign tasks may hurt the overall performance in Section \ref{randomassign}. 
Different from these works, SCache pre-schedules multiple shuffles without breaking load balancing.

>>>>

{\color{black}
\textbf{Modeling} 
% Most representative DAG computing frameworks use similar \textit{Bulk Synchronize Parallel} (BSP)\cite{valiant1990bridging} model to control data synchronization in each computing phase. 
% , i.e., \textit{stage} in Spark, \textit{superstep} in Pregel\cite{malewicz2010pregel} and so on. 
% (Hadoop MapReduce can also be considered as a special case of only one superstep in BSP model). 
% In the process of optimizing the shuffle phases between adjacent computing phases, we design a performance model to assist in analyzing computing process.
% There are also lots of performance models for MapReduce have been proposed, such as \cite{verma2011aria, khan2016hadoop, herodotou2011hadoop, chen2014cresp, farhat2016stochastic}.
% Verma et al. \cite{verma2011aria} proposed the ARIA model to estimate the required resources based on the job information, the amount of input data and a specified soft deadline.
Khan et al. \cite{khan2016hadoop} proposed the HP model which extends the ARIA model. The HP model adds scaling factors and uses a simple linear regression to estimate the job execution time on larger datasets.
% In \cite{herodotou2011hadoop}, Herodotou proposed a detailed set of mathematical performance models for describing the five phases of a MapReduce job and combine them into an overall MapReduce job model.
% The execution is separated into the phases: Read, Map, Collect, Spill, Merge, Shuffle, Merge, and Reduce. 
% The set of performance models describe each above-mentioned phases and combine into an overall MapReduce job model. 
Chen et al. \cite{chen2014cresp} proposed the CRESP model which is a cost model that estimates the performance of a job then 
% provisions the resources for the job.
Farshid Farhat et al.\cite{farhat2016stochastic} proposed a closed-form queuing model which focuses on stragglers and try to optimize them. 
% The proposed model is parameterized by the task inter-arrival times to the mappers, the delayed tailed service times, and the number of mappers, which is used to optimize the stragglers. 
% \cite{khan2016hadoop, farhat2016stochastic, chen2014cresp} have proposed several methods to model the DAG computing process.
However, the above models are not able to accurately describe the overhead caused by the shuffle process under different scheduling strategies. 
% Different from these models, our FRQ model quantifies computing and I/O resources and visualizes them in the time dimension. 
The FRQ model focuses on describing the overhead caused by the shuffle process in different scheduling strategies, which satisfies our demand.

@@

\textbf{Pre-scheduling} 
Slow-start from Apache Hadoop MapReduce is a classic approach to handle shuffle overhead. 
% Starfish \cite{starfish} gets sampled data statics for self-tuning system parameters (e.g. slow-start, etc). 
% DynMR \cite{dynmr} dynamically starts reduce tasks in late map stage. 
% All of them have the explicit I/O time in occupied slots. 
% SCache instead starts shuffle pre-fetching without consuming slots. 
iShuffle \cite{guo2017ishuffle} decouples shuffle from reducers and designs a centralized shuffle controller. 
% But it can neither handle multiple shuffles nor schedule multiple rounds of reduce tasks. 
iHadoop \cite{ihadoop} aggressively pre-schedules tasks in multiple successive stages to start fetching shuffle. 
% Besides \textit{slow-start} from Hadoop MapReduce, \cite{starfish, ihadoop, guo2017ishuffle, dynmr} have also proposed several methods to improve the DAG frameworks.
However, we have proved that randomly assigned tasks may hurt the overall performance in Section \ref{randomassign}. 
Different from these works, SCache pre-schedules multiple shuffles without breaking load balancing.
